---
title: "Mixed models for hi-Lo fish analysis"
author: "Fiona Francis"
date: "5/19/2021"
output: github_document
---
These are the data analyses for Jill Campbell's MSc chapter that complements the HiLo analysis for Sharon Jeffrey's invert data. This analysis examines the effect of current and other abiotic factors on fish abundance, biomass, and diversity at different sites in the Gulf Islands. THe data was collected slightly differently than the invertebrate data so the number of points and sites differ between the two studies. This project also involvles collaborators Sharon Jeffery (DFO), Sarah Dudas(DFO), and Francis Juanes(Uvic).

Jill used a total of 10 sites and recorded fish on transects at two depths at each site: 3 m and 15 m. Each site was visited 3 or 4 times over the season. Current speed was measured at each site over the course of one month and the analyses use the mean daily max current measures. Site will be included as a random effect in models. Abiotic factors are current speed, depth, rock cover.

```{r setup, include=FALSE}
## Load packages ---------------------------------------------------------
library(ggplot2)
library(grid)
library(gridExtra)
library(tidyverse)
library(lme4)
library(nlme)
library(bbmle)
library(AICcmodavg)
library(here)
library(sjPlot)
library(fishualize)

## read in data ------------------------------------------------------

data<- read_csv("FishData_Jan11.csv")
current <-read_csv("CurrentByDay.csv")
abiotic <- read_csv("transectdatawithallvariables.csv")
```

## Data summaries

```{r data clean up, include = F}

summary(data)
summary(current)
summary(abiotic)

## FISH DATA prep ---------------------------------------------------------

#summarize by site and replicate (this code is from J. Campbell FishAnalysis Jan 11)

Hisites <- c("Josef", "Burial", "Porlier", "Grainger")
Losites <- c("Coffin", "Snake", "Dragon", "McKenzie", "Anniversary", "Georgina")
fishdata <- data %>% 
  #Generate Weight values for each fish
  mutate(Weight = case_when(abSource == "DFO Haggarty and King 2004 Technical Report 2533" ~ a * (Length ^ b),
                            abSource == "California Fish and Game Fish Bulletin 177" ~ a * ((Length * 10) ^ b),
                            abSource == "NOAA 1978 Washington, Gowan, & Ito" ~ a * ((Length * 10) ^ b),
                            abSource == "FishBase" ~ 10 ^ (log10(a) + (b * log10(Length))))) %>% 
  #Create an identifier
  mutate(TransectID = paste(Site, TransectDepth, Replicate, sep = "_"),
         SiteID = paste(Site, TransectDepth, sep = "_"),
         Hi_Lo = case_when(Site %in% Hisites ~ "High",
                           Site %in% Losites ~ "Low"),
         Hi_Lo = factor(Hi_Lo, levels = c("High", "Low"), ordered = TRUE),
         Latin = factor(Latin),
         CurrDepth = paste(Hi_Lo, TransectDepth, sep = ""),
         CurrDepth = factor(CurrDepth, levels = c("High3", "High15", "Low3", "Low15"),
                            labels = c("High 3m", "High 15m", "Low 3m", "Low 15m"), ordered = TRUE)) %>% 
  #Remove replicate 4 from Georgina - influenced by nesting ling cod
  filter(TransectID != "Georgina_15_4",
         TransectID != "Georgina_3_4",
         Family != "Embiotocidae")

# Create a data frame with site richness, abundance, and biomass
fish <- fishdata %>% 
  group_by(Site, Hi_Lo, TransectDepth, CurrDepth, Replicate, SiteID, TransectID) %>% 
  summarize(Richness = length(unique(Latin)),
            Abundance = length(Length),
            Biomass = round(sum(Weight), 2)) %>% 
  mutate(Biomass_kg = Biomass/1000)

## CURRENT DATA prep ------------------------------------------------------------------------------------------
#we are using median max current speed for the prelimnary modelling so that it matches her other analyses

current <- current %>% group_by(logger) %>%
  summarize(CurrentMean = mean(SpeedMean), CurrentMin = mean(SpeedMin), CurrentMax = mean(SpeedMax), MedianMax = median(SpeedMax), meanCurrentSD = sd(SpeedMean), maxCurrentSD = sd(SpeedMax)) #note I think in her final summary Jill used the SD from ALL of the data when you need to calculate error around the the current sample size

current <- current %>% rename(Site = logger) %>% arrange(desc(CurrentMean))

# compare mean vs max in quick plot, need to decide what to use

ggplot(current) + geom_point(aes(CurrentMean, CurrentMax, colour = Site), size = 3) +
  theme_bw()

# slope and % rock varialbes

abiotic

# rename sites in abiotic to match fish
#abiotic <- abiotic %>% mutate(Site = replace(Site, (1:7), c("Burial", "Coffin","Dragon","Josef","McKenzie","Porlier","Snake")))

# merge abiotic with fish

data <- full_join(abiotic, current, by = "Site")
data <- data %>% rename(CurrentMax = CurrentMax.x) %>% select(-CurrentMean.y, -CurrentMax.y)

```

``` {r, echo = F}
data

# make depth a categorical value 

data <- data %>% mutate(TransectDepth = as.character(TransectDepth))

```

## Exploratory plots of abundance

### Plots of current and transect depth

```{r, fig.show="hold", out.width="50%", echo = F}

# abundance and current
ggplot(data) + geom_point(aes(CurrentMax, Abundance, colour = Site), size = 3, show.legend = F) +
    scale_color_fish_d(option = "Coris_gaimard", direction = -1) +  
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("Current Speed") +
  ylab("Abundance of fish") + 
  theme_bw()

#abundance and transect depth

ggplot(data) + geom_point(aes(TransectDepth, Abundance, colour = Site), size = 3, show.legend = F) +
    scale_color_fish_d(option = "Coris_gaimard", direction = -1) +  
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("Transect Depth (m)") +
  ylab("Abundance of fish")+ 
  theme_bw()

```

### Plots of slope and rock cover

```{r, fig.show="hold", out.width="50%", echo = F}
#abundance and slope

ggplot(data) + geom_point(aes(SlopeAngle, Abundance, colour = Site), size = 3, show.legend = F) +
    scale_color_fish_d(option = "Coris_gaimard", direction = -1) +  
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("Slope (degrees)") +
  ylab("Abundance of fish")+ 
  theme_bw()

#abundance and rock cover

ggplot(data) + geom_point(aes(PercRock, Abundance, colour = Site), size = 3, show.legend = F) +
    scale_color_fish_d(option = "Coris_gaimard", direction = -1) +  
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("% Rock") +
  ylab("Abundance of fish")+ 
  theme_bw()

```

## Same plots but of biomass instead of abundance

We are logging biomass to make the relationship more linear. 

### Plots of current and depth

```{r, fig.show="hold", out.width="50%", echo = F}

#abundance and slope

ggplot(data) + geom_point(aes(TransectDepth, log10(Biomass), colour = Site), size = 3, show.legend = F) +
    scale_color_fish_d(option = "Coris_gaimard", direction = -1) +  
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("Transect Depth") +
  ylab("Log biomass of fish")+ 
  theme_bw()

#abundance and rock cover

ggplot(data) + geom_point(aes(CurrentMax, log10(Biomass), colour = Site), size = 3, show.legend = F) +
    scale_color_fish_d(option = "Coris_gaimard", direction = -1) +  
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("Current") +
  ylab("Log biomass of fish")+ 
  theme_bw()

```

### Plots of slope and rock cover

```{r, fig.show="hold", out.width="50%", echo = F}

#abundance and slope

ggplot(data) + geom_point(aes(SlopeAngle, log10(Biomass), colour = Site), size = 3, show.legend = F) +
    scale_color_fish_d(option = "Coris_gaimard", direction = -1) +  
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("Slope (degrees)") +
  ylab("Log biomass of fish")+ 
  theme_bw()

#abundance and rock cover

ggplot(data) + geom_point(aes(PercRock, log10(Biomass), colour = Site), size = 3, show.legend = F) +
    scale_color_fish_d(option = "Coris_gaimard", direction = -1) +  
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("% Rock") +
  ylab("Log biomass of fish")+ 
  theme_bw()

```

# Plots of abundance, biomass, and richness

Just for interest sake, I don't know if the correlation between these dependent variables is important and needs to be considered? Food for thought.

```{r, fig.show="hold", out.width="50%", echo = F}
data %>% ggplot() + geom_point(aes(Richness, Abundance))
data %>% ggplot() + geom_point(aes(log10(Biomass), Abundance))

```

# Models of fish abundance

In all models site is included as a random factor and there are four variables (Transect depth, max daily current, slope, percent rock). We are looking at all combinations of variables but with no interactions.

```{r abundance, echo=T}

#one variable

Null.ab <- lme(Abundance ~ 1, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm1.ab <-  lme(Abundance ~ TransectDepth, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm2.ab <-  lme(Abundance ~ CurrentMax,
            random = ~ 1 | Site, data = data, method = "ML")

Lm3.ab <- lme(Abundance ~ SlopeAngle,
            random = ~ 1 | Site, data = data, method = "ML")

Lm4.ab <- lme(Abundance ~ PercRock,
            random = ~ 1 | Site, data = data, method = "ML")

#two variables

Lm5.ab  <- lme(Abundance ~ TransectDepth + CurrentMax, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm6.ab  <- lme(Abundance ~ TransectDepth + SlopeAngle, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm7.ab  <- lme(Abundance ~ TransectDepth + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm8.ab  <- lme(Abundance ~ SlopeAngle + CurrentMax, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm9.ab  <- lme(Abundance ~ SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm10.ab  <- lme(Abundance ~ PercRock + CurrentMax, 
            random = ~ 1 | Site, data = data, method = "ML")

#Three variables
Lm11.ab  <- lme(Abundance ~ CurrentMax + SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm12.ab  <- lme(Abundance ~ TransectDepth + SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm13.ab  <- lme(Abundance ~ TransectDepth + CurrentMax + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm14.ab  <- lme(Abundance ~ TransectDepth + CurrentMax + SlopeAngle, 
            random = ~ 1 | Site, data = data, method = "ML")
# four variables

Lm15.ab  <- lme(Abundance ~ CurrentMax + TransectDepth + SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")


bbmle::AICtab(Null.ab, Lm1.ab, Lm2.ab, Lm3.ab, Lm4.ab, Lm5.ab, Lm6.ab, Lm7.ab, Lm8.ab, Lm9.ab, Lm10.ab, Lm11.ab, Lm12.ab, Lm13.ab, Lm14.ab, Lm15.ab, base = T, weights = T, logLik = T)
```
## Diagnositics for model 7

There are three models that are within 2 AIC but we are going to explore the diagnostics of the first one (model 7) to see if it is even a decent model. 

``` {r model 7, echo = T}
# diagnostics for Lm7.ab

Lm7.ab

summary(Lm7.ab)

plot(Lm7.ab) # pretty cone shaped which isn't great

ggplot(data.frame(biomass=predict(Lm7.ab,type="link"),pearson=residuals(Lm1.ab,type="pearson")), # another way to visualize
       aes(x=biomass,y=pearson)) +
  geom_point() +
  theme_bw()

qqnorm(resid(Lm7.ab)) #decent

```

## Fitting a variance structure to model 7

Because there is a pretty obvious pattern in the residuals I am going to fit a variance structure to the model to see if this fixes this problem. I'll first fit it to model 7 and then if that corrects the skew I will fit the same structure to ALL of the original model set and then compare all of the models again.

```{R, echol = F}

Lm7.ab.var <- lme(Abundance ~ TransectDepth + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm7.ab.var <- update(Lm7.ab, weights = varExp(form = ~fitted(.)),method = "ML") # update model 7 with an exponential variance structure

Lm7.ab.var
plot(Lm7.ab.var)
qqnorm(Lm7.ab.var)

# rerun all models with new variance structure
Null.ab.var <- update(Null.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm1.ab.var <- update(Lm1.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm2.ab.var <- update(Lm2.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm3.ab.var <- update(Lm3.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm4.ab.var <- update(Lm4.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm5.ab.var <- update(Lm5.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm6.ab.var <- update(Lm6.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm7.ab.var <- update(Lm7.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm8.ab.var <- update(Lm8.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm9.ab.var <- update(Lm9.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm10.ab.var <- update(Lm10.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm11.ab.var <- update(Lm11.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm12.ab.var <- update(Lm12.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm13.ab.var <- update(Lm13.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm14.ab.var <- update(Lm14.ab, weights = varExp(form = ~fitted(.)),method = "ML")
Lm15.ab.var <- update(Lm15.ab, weights = varExp(form = ~fitted(.)),method = "ML")

bbmle::AICtab(Null.ab.var, Lm1.ab.var, Lm2.ab.var, Lm3.ab.var, Lm4.ab.var, Lm5.ab.var, Lm6.ab.var, Lm7.ab.var, Lm8.ab.var, Lm9.ab.var, 
              Lm10.ab.var, Lm11.ab.var, Lm12.ab.var, Lm13.ab.var, Lm14.ab.var, Lm15.ab.var, base = T, weights = T, logLik = T)
```

## Diagnostics for Model 13 (TransectDepth + CurrentMax + PercRock)

We are looking here at model 13 but there are 3 models (13, 7 and 15) which are all within 2 delta AIC. 
```{R, echo = T}
# diagnostics for Lm13.ab.var

Lm13.ab.var

summary(Lm13.ab.var)

plot(Lm13.ab.var)

ggplot(data.frame(biomass=predict(Lm13.ab.var,type="link"),pearson=residuals(Lm13.ab.var,type="pearson")),
       aes(x=biomass,y=pearson)) +
  geom_point() +
  theme_bw()

qqnorm(resid(Lm13.ab.var))


sjPlot::plot_model(Lm13.ab.var)

```

# Models of fish biomass

```{r biomass, echo=FALSE}
# hmm these don't actually look that bad haha, Lm1 is top which is not surprising as there is a ton of variation with depth in abundance

#one variable

Null.bio <- lme(log10(Biomass) ~ 1, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm1.bio <-  lme(log10(Biomass) ~ TransectDepth, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm2.bio <-  lme(log10(Biomass) ~ CurrentMax,
            random = ~ 1 | Site, data = data, method = "ML")

Lm3.bio <- lme(log10(Biomass) ~ SlopeAngle,
            random = ~ 1 | Site, data = data, method = "ML")

Lm4.bio <- lme(log10(Biomass) ~ PercRock,
            random = ~ 1 | Site, data = data, method = "ML")

#two variables

Lm5.bio  <- lme(log10(Biomass) ~ TransectDepth + CurrentMax, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm6.bio  <- lme(log10(Biomass) ~ TransectDepth + SlopeAngle, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm7.bio  <- lme(log10(Biomass) ~ TransectDepth + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm8.bio  <- lme(log10(Biomass) ~ SlopeAngle + CurrentMax, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm9.bio  <- lme(log10(Biomass) ~ SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm10.bio  <- lme(log10(Biomass) ~ PercRock + CurrentMax, 
            random = ~ 1 | Site, data = data, method = "ML")

#Three variables
Lm11.bio  <- lme(log10(Biomass) ~ CurrentMax + SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm12.bio  <- lme(log10(Biomass) ~ TransectDepth + SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm13.bio  <- lme(log10(Biomass) ~ TransectDepth + CurrentMax + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm14.bio  <- lme(log10(Biomass) ~ TransectDepth + CurrentMax + SlopeAngle, 
            random = ~ 1 | Site, data = data, method = "ML")
# four variables

Lm15.bio  <- lme(Biomass ~ CurrentMax + TransectDepth + SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

bbmle::AICtab(Null.bio, Lm1.bio, Lm2.bio, Lm3.bio, Lm4.bio, Lm5.bio, Lm6.bio, Lm7.bio, Lm8.bio, Lm9.bio, 
              Lm10.bio, Lm11.bio, Lm12.bio, Lm13.bio, Lm14.bio, Lm15.bio, base = T, weights = T, logLik = T)
```

## Looking at model 1 but again there are 4 models within 2 delta AIC (1, 6, 5, and 7). Depth is clearly very important but the other three models contain each of the other variables of interest.

```{r, echo = F}
Lm1.bio

plot(Lm1.bio)

qqnorm(Lm1.bio)

sjPlot::plot_model(Lm1.bio)

sjPlot::plot_model(Lm5.bio)

sjPlot::plot_model(Lm6.bio)

sjPlot::plot_model(Lm7.bio)


```


# Models of fish species richness

In all models site is included as a random factor and there are four variables (Transect depth, max daily current, slope, percent rock). We are looking at all combinations of variables but with no interactions.

```{r richness, echo=T}

#one variable

Null.r <- lme(Richness ~ 1, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm1.r <-  lme(Richness ~ TransectDepth, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm2.r <-  lme(Richness ~ CurrentMax,
            random = ~ 1 | Site, data = data, method = "ML")

Lm3.r <- lme(Richness ~ SlopeAngle,
            random = ~ 1 | Site, data = data, method = "ML")

Lm4.r <- lme(Richness ~ PercRock,
            random = ~ 1 | Site, data = data, method = "ML")

#two variables

Lm5.r  <- lme(Richness ~ TransectDepth + CurrentMax, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm6.r  <- lme(Richness ~ TransectDepth + SlopeAngle, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm7.r  <- lme(Richness ~ TransectDepth + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm8.r  <- lme(Richness ~ SlopeAngle + CurrentMax, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm9.r  <- lme(Richness ~ SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm10.r  <- lme(Richness ~ PercRock + CurrentMax, 
            random = ~ 1 | Site, data = data, method = "ML")

#Three variables
Lm11.r  <- lme(Richness ~ CurrentMax + SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm12.r  <- lme(Richness ~ TransectDepth + SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm13.r  <- lme(Richness ~ TransectDepth + CurrentMax + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")

Lm14.r  <- lme(Richness ~ TransectDepth + CurrentMax + SlopeAngle, 
            random = ~ 1 | Site, data = data, method = "ML")
# four variables

Lm15.r  <- lme(Richness ~ CurrentMax + TransectDepth + SlopeAngle + PercRock, 
            random = ~ 1 | Site, data = data, method = "ML")


bbmle::AICtab(Null.r, Lm1.r, Lm2.r, Lm3.r, Lm4.r, Lm5.r, Lm6.r, Lm7.r, Lm8.r, Lm9.r, Lm10.r, Lm11.r, Lm12.r, Lm13.r, Lm14.r, Lm15.r, base = T, weights = T, logLik = T)

plot(Lm7.r)

qqnorm(resid(Lm7.r))

```


## Length and depth relationships

Jill is interested in understanding how fish length changes in relation to species and in relation to depth. Are some species larger at deeper depths than others despite species differences? 

I think that this can be modeled in two ways. 

1) we fit a random effect for species where the slopes and intercepts vary by species to see if there is an overal effect of depth on fish size. I don't think that we need to worry about site ID as there would be no reason to expect fish to have different life history traits at different sites (would there)?

2) we can then look at species that have enough data to see how there are specific species that have a relationship with depth by fitting species as a fixed effect


``` {r, echo = F}


# Fit a model on all the data pooled together
fishdata <- fishdata %>% mutate(TransectDepth = as.character(TransectDepth))

fishdata <- fishdata %>% mutate(TransectDepth = recode(TransectDepth, '15' = "B", '3' = "A")) # changed these so that they would show up with 3 m as base since it is alphabetical in the model coefficients

fishdata <- fishdata %>% arrange(TransectDepth)

fishdata %>% ggplot() + geom_point(aes(TransectDepth, Length, colour = CommonName), show.legend = F)

fishdata %>% group_by(CommonName, Species) %>% summarise(n = n()) %>% print(n = Inf)

# running a random effect for fish species
null <- lme(log10(Length) ~ 1, 
            random = ~ 1 + TransectDepth| CommonName, data = fishdata, method = "ML")

m_partialpooled <- lme(log10(Length) ~ TransectDepth, 
                        random = ~ 1 + TransectDepth| CommonName, data = fishdata, method = "ML")

bbmle::AICtab(null, m_partialpooled, base = T, weights = T, logLik = T)

# summary of random effects model
summary(m_partialpooled)

plot(m_partialpooled)
qqnorm(resid(m_partialpooled))



#pull out the mean for each species from model
df_partial_pooling <- coef(m_partialpooled) %>% 
  as_tibble() %>% 
  rename(Intercept = `(Intercept)`, deep_depth = TransectDepthB) %>% 
  add_column(Model = "Partial pooling") %>% add_column(Subject = sort(unique(fishdata$CommonName)))

# pull out overall coefficient for depth 

coef(summary(m_partialpooled))

# Repeat the mean for each species
df_pooled <- tibble(
  Model = "Complete pooling",
  Subject = unique(fishdata$CommonName),
  Intercept = coef(summary(m_partialpooled))[1], 
  deep_depth = coef(summary(m_partialpooled))[2]
)
df_pooled


# combine coefficients for plotting 

df_models <- left_join(df_pooled, df_partial_pooling, by = "Subject")

# quick and direty plot of coefficients
df_models %>% ggplot() + geom_point(aes(Intercept.x, Subject), colour = "grey") + geom_point(aes((Intercept.x+deep_depth.x), Subject), colour = "pink") +
  geom_point(aes((Intercept.y+deep_depth.y), Subject), colour = "red", size = 2) + geom_point(aes(Intercept.y, Subject), colour = "black", size = 2) + 
  xlab("log mean Length") +
  ylab("Fish species")+ 
  theme_bw()

```
